My Past Work

### 2025-01-28 interests.qmd
Update

This project emphasized enabling users to focus on content creation while saving time with AI-driven slide suggestions​

@@

### (2) GPTDashboard - Desktop and Mobile View

@@

<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&amp;node-id=1-155&amp;starting-point-node-id=1%3A155&amp;embed-host=share" allowfullscreen>

@@

This project tackled the challenges of decision fatigue and financial strain by providing actionable guidance in a visually engaging way​

>>>>

This project emphasized enabling users to focus on content creation while saving time with AI-driven slide suggestions.

@@

### (2) GPTDashboard - Desktop View

@@

@@

This project tackled the challenges of decision fatigue and financial strain by providing actionable guidance in a visually engaging way.
